\documentclass[a4paper,12pt]{article}

\title{NaNoWriMo Dares}
\date{}

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french]{babel}
\usepackage{charter}  % <3
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\newcommand{\bi}{\section{---------------------------------------}\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\todo}{\item[$\square$]}
\newcommand{\done}{\item[$\blacksquare$]}

\usepackage[cm]{fullpage}

\begin{document}
\maketitle

\bi
\todo Make your characters play 'The Game.'
\todo BP\footnote{Bonus points.} if someone says, "I lost the game" at the climax.
\todo DBP\footnote{Double bonus points.} if the game is a plot point.
\todo TBP\footnote{Triple…} if the game isn't ever explained.
\ei

\bi
\todo A character has a journal.
\todo BP: Then other characters find it
\todo DBP: They start writing in it.
\ei

\bi
\todo A game of I Have Never
\todo BP: There's a character who has never done any of the things stated.
\todo DBP: There's a character who's done ALL of them.
\todo TBP: This is a vital plot point or turning point.
\ei

\bi
\todo Include a funny discussion about suicide.
\ei

\bi
\todo Include a karaoke contest
\todo BP: A character doesn't want to sing but is forced into it.
\todo DBP: That character wows everyone with their amazing voice.
\todo TBP: The villain uses this event against the protagonist.
\ei

\bi
\todo 10 hours of Nyancat
\todo BP if this is used as a cruel and unusual punishment.
\ei

\bi
\todo An entry from fmylife.com actually happening to a character
\ei

\bi
\todo An RPG style battle
\todo BP if one of the characters dies
\todo DBP if anotheer character tries to heal them using phoenix down
\todo TBP if it works
\ei

\bi
\todo Massive party in the middle of a tense scene.
\todo BP if everyone from the villain to the super-minor characters are invited.
\todo BP if a super-minor character doesn’t show up and it makes everyone upset.
\todo DBP if the punch is spiked.
\todo TBP if the villain reveals his whole evil plan while totally sloshed but in the morning nobody remembers it.
\ei

\bi
\todo Exploring an abandoned building.
\todo BP if it’s the wrong abandoned building.
\ei

\bi
\todo A character calls a relative they haven’t talked to in ages to borrow something. (Not money!)
\todo BP if it's a shovel
\todo DBP if the relative is a Mr Ian Woon
\todo TBP if the character actually returns the item
\ei

\bi
\todo Suddenly, \_\_\_ ! (ducks, vodka, etc.)
\todo BP if it's pineapples
\ei



\bi
\todo If a character considers bungee jumping
\todo TP if they actually do it
\todo TBP if they convince someone to do it with them
\todo TBP if they figure out the crucial element of the plot while bungee jumping
\todo Ttarbucks points if YOU go bungee jumping for the sake of research.
\ei

\bi
\todo Tave characters randomly quote the hogwarts sorting hat songs.
\todo + if it makes sense in context.
\todo ++ if it is central to the plot.
\ei

\bi
\todo include a character with a social networking addiction.
\todo + if they stop at crucial points in the plot to update facebook/twitter/tumblr/whatever.
\todo ++ if they do this at the most inopportune moments possible.
\todo +++ if, while doing this, they say things like “wait! my facebook friends/followers/etc. would think this is HILARIOUS.”
\todo ++++ if they say this in the middle of a beheading.
\ei


\bi
\todo Have a character copyright a novel, music or videogame they made...
\todo BP if everyone downloads it for free anyway
\todo DBP if its not his concept
\todo TBP if they get into a copyright war with the real one
\todo QBP if the thing never even was copyrighted by anyone
\ei


\bi
\todo Have a character killed by the Travelling Shovel of Death (but that's hardly a dare! WAIT, interrupting parenthesis) and explicitly identify it as the Travelling Shovel of Death.
\todo BP if the shovel-ee is otherwise immortal and can only be killed by a metafictional artifact.
\todo DBP if the plot involves a quest to acquire the Travelling Shovel of Death.
\todo TBP if this quest involves visits to the Nanovels of other Nanoers using the Travelling Shovel of Death.
\todo QBP if you type the name of the Travelling Shovel of Death out in full every time that you refer to the Travelling Shovel of Death.
\todo SBP if your nanovel is an academic history of NaNoWriMo itself using the quest for the Travelling Shovel of Death as a framing device.
\todo BNP if the person killed with the Shovel is a white supremacist.
\ei


\bi
\todo Have a character meet Jenny Everywhere\footnote{http://en.wikipedia.org/wiki/Jenny\_Everywhere}.
\todo +BP: Have Jenny Everywhere be a major character.
\todo +DBP: Have Jenny's universe-shifting powers be explained.
\todo +TBP: Make her powers a major plot point.
\ei


\bi
\todo I dare you to have a pivotal plot event occur while the MC is in the bath.
\todo BP if he/she has to get out of the bath right away to deal with it
\todo DBP if he/she doesn't have any time to dry off or put any clothes on
\todo TBP if nobody seems to notice
\todo QBP if EVERYONE notices and it grinds the plot to a halt right in the middle of a turning point
\todo Cookies if the plot is then interrupted by the character sustaining some kind of injury due to being naked, such as frostbite.
\ei



\bi
\todo I dare you to have a character with an eye-patch
\todo +If the eye-patch is on a different eye in every scene.
\todo ++If the eye under the eye patch is wounded every time
\todo +++If no one notices
\ei



\bi
\todo Kill your protagonist in every scene.
\todo BP if nobody notices.
\todo DBP if it's never explained why or how that happens.
\todo TBP if it is nevertheless intrinsic to the plot.
\ei



\bi
\todo Have a character who wears shoes which are two different colours but still from the same brand in the same model, to know which directions are right and left.
\todo BP: If it is a REALLY UGLY combination, not just like white/black, red/pink, BUT GREEN/PINK, PURPLE/ORANGE and so on.
\todo DBP: If the character’s shoes at one points are so worn out, that (s)he has to wear the opposite shoes, which (s)he has hidden since (s)he started using the system.
\todo TBP: If this makes the character completely confused about directions and at some point gets totally lost.
\ei


\bi
\todo Name all of your characters with anagrams of Ian Woon.
\todo BP: If you also have important plot objects named with an anagram (Like a Win a Moron contest. )
\todo DBP: If no one notices this in the story.
\todo TBP: If everyone notices this in the story and makes fun of it.
\ei

\bi
\todo Have someone mention that so many people complain about the weather, but no one ever actually \emph{does} anything about it.
\todo BP if someone is planning on trying do something about the weather.
\todo DBP if this is a Quest.
\todo TBP if one person succeeds just enough to end up with a personal raincloud. Not as many bonus points if someone succeeds enough to have his/er own, personal weather, independent from everyone else's -- but s/he can't control it.
\todo Additional Fun: Make that person's weather controlled by someone else entirely. Like, say, the Bad Guy.
\ei


\bi
\todo Have someone point out that it's not possible to slam a revolving door.
\todo Bonus points if s/he is telling someone who is trying to do just that.
\ei


\bi
\todo "Clearly, this calls for a clown car."
\todo BP: If the situation really does call for a clown car.
\todo DBP: If a clown car is brought in.
\todo TBP: If there are clowns inside the clown car.
\todo QBP: If the clowns become significant somehow.
\ei



\bi
\todo The character swap! Get permission from friends to have their characters make cameo appearences in your book!
\todo BP if you have real people make cameo appearences.
\todo DBP if you can convince one of them to let you kill them off! <3
\ei


\bi
\todo Have characters quarrel over "pop vs. soda"
\todo BP if it's the hero and the villian.
\todo DBP if that's what started their rivalry.
\todo TBP if it turns into an all-out war.
\ei



\bi
\todo Include a character that uses the word "hetero" as some people use the word "gay". For example, "That soda machine is so hetero; it took my dollar and then not only did it give me the wrong soda, but it didn't give me any change."
\ei


\bi
\todo Have your character have a special recognisable pen he likes to use.
\todo Have this pen covertly stolen by another character.
\todo BP: This pen is repeatedly stolen by other characters
\todo DBP: Every important character is, at some point, shown using this pen.
\todo TBP: There is a clear chain of thefts. ie. The Big Bad originally owned this pen, but it was stolen by Henchman. Guard then stole it. The Mole took it off him, etc.
\todo QBP: This is intergral to the plot.
\ei


\bi
\todo Incorporate the line "Sorry about your coffee, I had to throw it at someone."
\todo Bonus points if it's said to the main character
\todo Double bonus points if it's said BY the main character
\todo Triple bonus points if it was thrown at the love interest
\todo Quadruple bonus points if they didn't miss
\todo Quintuple bonus points if the main character later gets a coffee in the face
\ei


\bi
\todo Include a ghost that isn't unfriendly, isn't particularly friendly either, doesn't communicate much with the living, and just generally tolerates the people living in his house.
\todo BP if he turns on the radio, just because he likes music
\todo DBP if he takes occasional showers
\todo TBP if the people living in his house (or place or whatever) know about him, and just say "Oh yeah, that was the ghost" like it's nothing weird
\ei

\bi
\todo Include:
\item Character A: Why would you think I don't like you?
\item Character B: You sent ninja assassins to kill me. Twice.
\item Character A: I said I was sorry.
\todo BP if character A really did hire ninja assassins
\todo DBP if character A is your MC
\todo TBP if the assassination attempts are completely justifiable
\todo QBP if characters A and B hook up at the end of your novel
\ei


\bi
\todo Have someone that is always in the elevator every time your characters use one.
\todo BP if they don't think it's odd
\todo DBP if at some point s/he becomes relevant
\todo TBP if, at that point, s/he is /not/ in the elevator, and your characters have to go haring off after the elevator character.
\ei


\bi
\todo I dare you to include characters dancing to Psy - Gangnam Style!
\todo BP if it's the main character
\todo DBP if Everyone does it
\todo TPB if Psy appears and people start dancing along wih him.
\ei



\bi
\todo A character always orders the same drink in any bar: a glass of milk with an ice cube in it.
\todo BP: If this character has an elaborate and long-winded explanation for this odd preference.
\todo DBP: If this explanation is at least 1,667 words long.
\ei

\bi
\todo A character loves to cook but apparently has no sense of taste; everything s/he makes is revolting.
\todo BP: If this character accidentally invents something really, really tasty.
\ei

\bi
\todo A character believes s/he was a prehistoric hunter-gatherer in a past life and is constantly comparing modern life with the way things "used to be".
\todo BP: If s/he professes to prefer mammoth to beef.
\ei

\bi
\todo A character is a competitive facial-hair grower.
\ei


\bi
\todo A character enters a battle or fight armed only with a stapler.
\todo BP: If the character is really, really good with the stapler.
\todo DBP: If the character singlehandedly wins with the stapler.
\todo TBP: If the character is later defeated by an enemy with a paperclip.
\ei


\bi
\todo Include a Siri-esqe smartphone app that's incredibly snarky. (I envision it like if GLaDOS was an app.)
\todo BP if the app never lets the character look up things it finds "unnecessary" or that it looks down upon for some reason.
\todo DBP if it refuses to search for something unless you ask nicely.
\ei

\bi
\todo Have one of your female characters start PMS-ing at some point.
\todo Bonus points if she’s previously been really sweet and nice.
\todo DBP if she yells at the villain.
\todo TBP if it makes the villain cry.
\ei

\bi
\todo Have a pineapple as a murder weapon.
\ei


\bi
\todo Have your villain pursue some really random, unexpected hobby. Say, knitting.
\todo Bonus points if the villain’s really bad at it.
\todo DBP if the villain has an emotional breakdown because of this.
\todo TBP if your MC comforts them because your MC also pursues that hobby and is really good at it.
\todo QBP if it’s the other way around – your villain comforts your MC after your MC had an emotional breakdown about their failings of knitting.
\ei

\bi
\todo Have your characters start quoting Lady Gaga songs.
\todo Bonus points if it makes sense in the context.
\todo DBP if they’re completely serious.
\todo TBP if they don’t even realize they’re doing it.
\todo QBP if they live in a time period or alternate universe where Lady Gaga doesn’t exist.
\todo 5BP if they’re wearing extremely odd outfits while they’re doing so.
\todo 6BP if there’s a completely logical reason for your characters to be wearing them.
\ei

\bi
\todo Have two characters get into a completely serious duel with food items as weapons.
\ei

\bi
\todo Dare: Your characters go on a road trip that basically includes the passengers shouting "LEFT!" or "RIGHT" at the turns.
\todo BP: If your characters end up in the middle of a field.
\todo DBP: If your characters manage to take a whole chapter finding their way home.
\todo TBP: If they end up at the villain's hideout by accident, therefore capturing the evil one.
\ei

\bi
\todo Let your quietest character (main or not) have the biggest secret. BP if it's a dangerous secret. TBP if they've been hiding it since WAY before the novel started.
\ei

\bi
\todo Have something a character reads or writes on the inside of a bathroom stall turn into a major plot point.
\ei


\bi
\todo "Have a main character who’s a ghost, but have this fact not affect the story at all, other than maybe a few comments from the other characters.
\todo Bonus points if it’s in a world where no one believes in ghosts."
\ei


\bi
\todo Have a main character who has an unusual nick name that EVERYONE calls them by, even when it's not appropriate to be using nicknames (like school registers, doctor's appiontments, etc)
\todo BP if their real name incredibly plain and kind of forgettable.
\todo DBP if no one can seem to remember that name off hand.
\todo TBP if all instances of that name written down are smudged, erased, or rendered illegible for no explainable reason.
\todo QBP if anyone who knows their normal name and tries to said it is constantly cut off, silenced, faints dramatically or is horribly killed when they're about to utter it.
\todo \todo SBP if the name is integral to the plot somehow.
\todo \todo A cookie if the name is revealed in the final paragraph.
\todo \todo A chocolate fish if no one knows where the nickname came from ANYWAY.
\ei


\bi
\todo \todo Have your characters play a game of One Thousand Blank White Cards. If you don't know how it's played, the explanation is here:
\todo \todo http://www.geocities.com/nconner23/bwcards.html
\ei


\bi
\todo \todo Have your main characters get stuck in a traffic jam on their way to Meet the Evil Nemisis at You-Know-Where for the Final Showdown so they can Save the World.
\todo \todo + if the villain rides past on a bicycle
\todo \todo ++ if your story is set in a time period when neither cars nor bicycles are invented
\todo \todo +++ if the villain rides through the traffic at the exact moment that it finally moves-- and gets hit
\ei


\bi
\todo All the chapters in your story are the titles of Beatles songs
\todo DB- there is at least one line from the song somewhere in the chapter
\todo TP- the chapter is relevant (or can be related) to the the title
\todo QP- The climax occurs in a chapter entitled "I Am The Walrus"
\todo x5 - Your MC's names are taken from the songs
\todo infinite points- You have auxiliary characters named John, Paul, George, and Ringo
\ei


\bi
\todo I dare you to have a food fight in your novel.
\todo Bonus points if it's essential to the plot.
\todo Extra bonus points if it takes place somewhere unusual for a food fight -- the royal banquet hall, a 5-star restaurant, a wedding reception, etc.
\todo A cookie if you top 2k with a detailed description of the food fight.
\ei


\bi
\todo I dare you to solve a problem McGyver style, using only a rubber-band, a paperclip and toothpaste.

\bi
\todo I dare you to include a character named Someone.
\todo Bonus if his name is equally nondescript
\todo A cookie if no one ever gets confused except ONE CHARACTER, and no one ever understands how that one character gets confused.
\ei


\bi
\todo One of your characters always says “Thank you for calling
\todo Dominoes, how may I help you” every time they pick up the phone (instead
\todo of Hello).
\ei


\bi
\todo Include the prophecy: The people will go to the place and do the thing that will have the consequence.
\ei


\bi
\todo Have a character who has a camera with him/her at all times, and takes a picture of every new person he/she meets. (I just think it would be cool)
\todo +BP - if the photos come in handy later in the story.
\ei


\bi
\todo Have a side character who is always "running from the government" whenever he/she crosses paths with your MC.
\todo +BP - if at one point, your MC is really running from the government when he crosses paths with the side character.
\todo ++DBP - if you actually see the side character being chased by agents at one point toward the end, revealing that he/she was telling the truth all along.
\ei


\bi
\todo Have your novel 'sponsored'. Be sure to have a 'commercial break' right before something really important happens.
\todo BP if the characters say "After the break."
\todo DBP if there is also lots of clumsy product placement throughout.
\todo TBP if a character stops in the middle of the action to deliver a sales pitch.
\todo QBP if this character says "And if you call now, we'll throw in an author interview and a set of book-group questions at no extra cost!"
\ei

\bi
\todo Ninja kittens
\todo BP if they are actually a threat/menacing to your characters
\todo DBP if they are still actually cute fluffy kittens (and not some weird ninja cat creature)
\ei

%LOL
\bi
\todo Include a character that speaks entirely in alphabetical order.
\todo Ex: Like talk they this would. Annoying is not this?
\todo BP: If everyone understands him/her.
\todo DBP: If everyone understands save your main character.
\todo TBP: If it catches on with other characters.
\todo QBP: If the narrations follow the same pattern.
\ei


\todo One of your characters gets infected with a somewhat harmless, but annoying alien disease.
\todo BP: if the disease turns the character purple.
\todo DBP: if the cure only makes it worse.
\todo TBP: If the purple skin color turns out to be an advantage at some point in the story.
\ei


\bi 
\todo A household object (toaster, football, vase) turns out to strongly resemble an alien idol.
\todo BP: This starts a serious theological discussion between the owner of the object and the alien(s). (Ooh, lots of words to be found here!)
\todo DBP: The aliens are offended by the use of the object.
\todo TBP: This blasphemy sours diplomacy between humans and the aliens.
\ei

\bi
\todo One of your dumber characters (major or minor) comes up with a solution to a seemingly insurmountable scientific/technological problem.
\todo BP: They manage it in minutes, much to the chagrin of the smarter characters who have been puzzling over it for hours.
\todo DBP: The smarter characters ignore his solution and continue trying to coming up with their own and failing.
\todo TBP: The most intelligent of the characters finally figures it out after a long period of deep thought. It's exactly what the other character said.
\todo Cookies: The delay negatively affects the plot and becomes a major turn in character development for everyone involved.
\ei 


\end{document}